Final Report

### 2022-05-07 Final Report.Rmd
took out weird text

```{r}
#North America 1996-2006
north_96 <- na.omit(north_america)  %>% 
  group_by(country) %>% 
  filter(year == 1996) %>% 
  summarize(avg_deaths_96 = mean(total_deaths))

@@

#South America
south_96 <- na.omit(south_america)  %>% 
  group_by(country) %>% 
  filter(year == 1996) %>% 
  summarize(avg_deaths_96 = mean(total_deaths))

@@

=======
kable(list(south_96,south_01,south_06), caption = "South America Deaths 1996-2006")

south_07 <- na.omit(south_america)  %>% 
  group_by(country) %>% 
  filter(year == 2007) %>% 
  summarize(avg_deaths_07 = mean(total_deaths))
>>>>>>> b277bd1eb5761b57f0819d4f702030583bbe3739

@@

kable(list(africa_07,africa_12,africa_17), caption = "Africa Deaths 2007-2017")

deaths_oceania <- na.omit(oceania)  %>% 
  group_by(country) %>% 
  summarize(oceania_deaths = mean(total_deaths))
```
***

>>>>

```{r}
#1996-2006
north_96 <- na.omit(north_america)  %>% 
  group_by(country) %>% 
  filter(year == 1996) %>% 
  summarize(avg_deaths_96 = mean(total_deaths))

@@

south_96 <- na.omit(south_america)  %>% 
  group_by(country) %>% 
  filter(year == 1996) %>% 
  summarize(avg_deaths_96 = mean(total_deaths))

@@

kable(list(south_96,south_01,south_06), caption = "South America Deaths 1996-2006")

south_07 <- na.omit(south_america)  %>% 
  group_by(country) %>% 
  filter(year == 2007) %>% 
  summarize(avg_deaths_07 = mean(total_deaths))

@@

kable(list(africa_07,africa_12,africa_17), caption = "Africa Deaths 2007-2017")
```
***
